On Secure Delegation of SampBQP with a Classical Client

### 2020-02-09 bqp.tex
Add the other parallel rep paper
Give more protocols names

@@

We give a high-level overview of the compiliation results. \Ethan{Maybe just delete it and give name only}

\begin{protocol}{\Cref{proto:BlindBQP} compiled using Mahadev's measurement protocol \Ethan{Give this a name}}
	\label{proto:QPIP0BQP}
	\begin{enumerate}
		\item The verifier generates $\Lambda, \Lambda', pk, sk, evk, ct_x$ the same way as in \cref{proto:BlindBQP}. \Ethan{Need more notation? But how?}
			Then, using $\Lambda'$, it generates $k, td$.
			It sends $k, evk, ct_x$ to the prover.
		\item The prover, on inputs $k, evk, ct_x$, generates classical ``commitment" $y$ and internal state $\ket{st}$.
			It sends $y$ to the verifier.
		\item The verifier sends the prover a public coin $c\in\set{0,1}$.
		\item The prover, on inputs $c$ and $\ket{st}$, generates classical $a$ and sends it to the verifier.
		\item The verifier, on inputs $k, td, y, c, a, sk$, generates and outputs either $acc$ or $rej$.
	\end{enumerate}
\end{protocol}

@@

\begin{thm}
	\cref{proto:repQPIP0BQP} has negligible completeness and soundness
\end{thm}
\begin{prf}
	See \cite{parallelrep} \Ethan{TODO FIND AND CITE the other parallel rep. paper}
\end{prf}

@@

	Suppose without loss of generality that the verifier knows $f(x)$ is of length $m=\poly(n)$ \Ethan{Seems like a strong assumption; maybe need to explain how?}
	\begin{enumerate}
		\item Run \cref{proto:repQPIP0BQP} for all $L\in\cL$ in parallel using input $x$. The verifier gets outputs $v_{i, b}\in\set{Acc, Rej}$.
		\item If $\exists i$ s.t. $v_{i,0}=v_{i,1}$, reject.
		\item Otherwise, define $y_i = b$ where $v_{i, b}=Acc$. This gives $y\in\set{0,1}^m$
		\item Verifier outputs $y$
	\end{enumerate}
\end{protocol}

>>>>

\def\bz{\mathsf{blind, 0}}
\nc{\Pibz}{\ensuremath{\Pi_\bz}}
\nc{\Vbz}{\ensuremath{V_\bz}}
\nc{\Pbz}{\ensuremath{P_\bz}}

\def\bzrep{\mathsf{blind, 0, rep}}
\nc{\Pibzrep}{\ensuremath{\Pi_\bzrep}}

@@

We give a high-level overview of the compiliation results.

\begin{protocol}{Blind $\QPIP_0$ protocol $\Pibz$ for $BQP$ language $L$}
	\label{proto:QPIP0BQP}
	\begin{enumerate}
		\item The verifier generates $\Lambda, \Lambda', pk, sk, evk, ct_x$ the same way as in \cref{proto:BlindBQP}. \Ethan{Need more notation? But how?}
			Then, using $\Lambda'$, it generates $k, td$.
			It sends $k, evk, ct_x$ to the prover.
		\item The prover, on inputs $k, evk, ct_x$, generates classical ``commitment" $y$ and internal state $\ket{st}$.
			It sends $y$ to the verifier.
		\item The verifier sends the prover a public coin $c\in\set{0,1}$.
		\item The prover, on inputs $c$ and $\ket{st}$, generates classical $a$ and sends it to the verifier.
		\item The verifier, on inputs $k, td, y, c, a, sk$, generates and outputs either $acc$ or $rej$.
	\end{enumerate}
\end{protocol}

@@

\begin{thm}
	\cref{proto:repQPIP0BQP} has negligible completeness and soundness
\end{thm}
\begin{prf}
	See \cite{parallelrep, alagic2019twomessage}
\end{prf}

@@

	Suppose without loss of generality that the verifier knows $f(x)$ is of length $m=\poly(n)$ \Ethan{Seems like a strong assumption; maybe need to explain how?}
	\begin{enumerate}
		\item Run $\Pibzrep$ for all $L\in\cL$ in parallel using input $x$. The verifier gets outputs $v_{i, b}\in\set{Acc, Rej}$.
		\item If $\exists i$ s.t. $v_{i,0}=v_{i,1}$, reject.
		\item Otherwise, define $y_i = b$ where $v_{i, b}=Acc$. This gives $y\in\set{0,1}^m$
		\item Verifier outputs $y$
	\end{enumerate}
\end{protocol}
